% LaTeX resume using res.cls

\documentstyle[line,margin,hyperref]{res}
% Use \documentstyle[line,margin,newcent]{res} to get New Century
% Schoolbook Postscript font 
% Use \documentstyle[line,margin]{res} to get default (Computer Modern) font 
%\renewcommand{\namefont}{}

\begin{document}

\name{{\LARGE \textit{Katie Hoffman}}}
% \address used twice to have two lines of address
%\address{90 Norfolk Street \#2, Cambridge, MA 02139}
\address{\begin{tabular}{lcr}Brooklyn, NY&720.232.7274&\href{mailto:ktahoffman@gmail.com}{ktahoffman@gmail.com}\end{tabular}}
 
\begin{resume}

\section{Jobs}

{\bf aParently}\hfill August 2015 - Present \\
\textit{Full Stack Web Developer}\\
Building interactive communication and calendar Rails app\\
for parents and schools. 

{\bf Flatiron School}\hfill April 2014 - July 2015 \\
\textit{Senior Instructor}\\
Developed test-driven Ruby and JavaScript curriculum\\
and led lessons and code reviews.

{\bf Beta NYC}\hfill March 2014 - April 2014 \\
\textit{Extern Developer}\\
Munged open government project CSV to serve JSON\\
to an \href{http://www.opengovtimeline.com/}{{interactive timeline}}.

{\bf Brooklyn Free School}\hfill Aug. 2013 - Nov. 2013 \\
\textit{After School Teacher}\\
Created and implemented lesson plans to encourage \\
literacy and math skills.

{\bf Mountain Friends Camp}\hfill June - Aug. 2013 \\	
\textit{Camp Counselor}\\
Developed and co-­executed the Counselor ­in \\
­Training curriculum.

\section{Schools}

{\bf Flatiron School} \hfill April 2013 \\
New York Web Development Fellow

{\bf Columbia University} \hfill May 2011 \\	
 \textit{Barnard College}\\
B.A. Psychology, Minor in Biology\\
Graduated with Distinction

\section{Projects}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } llr}
\href{https://kthffmn.github.io/two-dots/}{{\bf Two Dots}} &Simple JS implementation of the popular app &May 2015\\
\href{https://kthffmn.github.io/aviator/}{{\bf Aviator}} & Up and down key plane game &June 2015\\
\href{https://kthffmn.github.io/sphearical/}{{\bf Sphearical}}&Map of most streamed songs on Spotify&May 2014\\
\href{https://kthffmn.github.io/whac-a-mole/}{{\bf Whac-A-Mole}}&jQuery mimic of the 70's arcade game &Nov. 2014\\
\href{https://tic-tac-toe-minimax.herokuapp.com/}{{\bf Tic-Tac-Toe}}&Minimax algorithm on Sinatra &July 2014
\end{tabular*}

\section{Publications}

\href{http://kthffmn.github.io/blog/2016/02/08/html-bouncing-ball-using-nested-marquees/}{{\textit{Marquee Element}}} (Feb. 2016) \href{https://kthffmn.github.io}{{kthffmn.github.io}}

Howlett, N., Hoffman, K., et. al. \href{https://bmcgenomics.biomedcentral.com/articles/10.1186/1471-2164-13-211}{{\textit{Identification of chemosensory receptor genes in Manduca sexta and knockdown by RNA interference}}}. BMC Genomics, May 2012.
 
\section{Technologies}

%\textit{Selected Languages and Technologies:}\\
%\begin{tabular}{l}
Ruby (RSpec), Rails (Capybara), JavaScript (Jasmine), jQuery, HTML, CSS, SQL, Git,
\LaTeX, Markdown, SPSS

\section{Interests}

Improv, sketch, stand-up, comedic acting

%\end{tabular}\\\\
%\textit{Selected coursework:}\\
%\begin{tabular}{lll}
%Computability&Completeness&Algebraic topology\\
%Nonlinear dynamics&Distributed systems&Machine learning\\
%Artificial intelligence&Software engineering&Natural language processing\\
%Bayesian learning&Microcontrollers&Complex analysis
%\end{tabular}

\end{resume}
\end{document}